\documentclass[14pt]{beamer}
\input{../../../beamer-preamble-2020}
\usetheme{default}
\usecolortheme{seahorse}


\title[] {Factoring Trinomials with 1 as Leading Coefficient}
\author{Jonathan R. Bacolod}
\institute[SHS]{Sauyo High School}
\date{}

\begin{document}
	\frame{\titlepage}
	
	\begin{frame}
		\frametitle{What are General Trinomials?}
		When you multiply two binomial factors which are not
		identical, the result is a quadratic trinomial or general trinomial.
	\end{frame}
	
	\begin{frame}
		\frametitle{What are General Trinomials?}
		An expression in the form $$ ax^2 + bx + c $$ where $ a $, $ b $, and $ c $ are integers is called general trinomial.
		
		$ a $ is the leading coefficient, $ bx $ is the middle term, and $ c $ is the constant term.
	\end{frame}

    \begin{frame}
    	\frametitle{What are the Types of General Trinomials?}
    	
    	\begin{enumerate}
    		\item<1-> Trinomial in the form of $ ax^2 + bx + c $, where $ a=1 $
    		\item<2-> Trinomial in the form of $ ax^2 + bx + c $, where $ a \neq 1 $
    	\end{enumerate}
    \end{frame}
	
    \begin{frame}
    	\frametitle{How to Factor Trinomials with 1 as Leading Coefficient?}
    	\begin{enumerate}
    		\item<1-> Factor out the greatest common monomial of all terms of the given trinomial.
    		\item<2-> List the factors of the last term ($ c $).
    		\item<3-> Find two factors with a product equal to the last term ($ c $) and a sum equal to the middle term ($ b $).
    		\item<4-> Write the factored form of the trinomial following the pattern $$(x+ \text{first factor}) (x+ \text{second factor})$$.
    	\end{enumerate}
    \end{frame}

    \begin{frame}
    	\begin{center}
    		\textbf{\LARGE Thank you for watching.}
    	\end{center}
    \end{frame}
	
\end{document}