\input{../../worksheets-preamble-2020}

\def \Lesson {Rational Algebraic Expressions}
\def \QuizCode {4}

\begin{document}
	\begin{center}
		\textbf{\large Quiz \#\QuizCode: \Lesson}
	\end{center}

    \vspace*{2em}

    \noindent \textbf{A. Similar or Dissimilar} 
    
    Write Similar if the given fractions are similar or Dissimilar if they are dissimilar. One point each.
    
    \begin{enumerate}
    	\begin{multicols}{2}
    		\item $ \dfrac{1}{4} $ and $ \dfrac{3}{4} $
    		\item $ \dfrac{1}{6} $ and $ \dfrac{1}{5} $
    		\item $ \dfrac{5}{3} $ and $ \dfrac{2}{3} $
    		\item $ \dfrac{4}{7} $ and $ \dfrac{4}{5} $
    		\item $ \dfrac{6}{5} $ and $ \dfrac{1}{5} $
    	\end{multicols}
    \end{enumerate}

    \vspace*{1.3ex}

    \noindent \textbf{B. Adding and Subtracting Rational Expressions} 
    
    Perform the indicated operation. Choose the answer from the box. Write the letter only. One point each.
    
    \begin{center} \fbox{\fbox{\parbox{5.5in}{\centering \begin{enumerate}[label=\alph*. ]
    					\begin{multicols}{2}
    						\item  $ \dfrac{2x + 7}{3x - 6} $
    						\item  $ \dfrac{2x + 6}{(x + 1)(x + 2)} $
    						\item  $ \dfrac{7 x^{2} + 52 x - 53}{3(x + 8)(x - 1)} $	
    						\item  $ -\dfrac{1}{x^3} $
    						\item  $ \dfrac{50 + 12x}{3x(x + 4)} $	
    						\item  $ -\dfrac{1}{2x^2 + 13x + 20} $
    						\item  $ \dfrac{42x^2 + 137x - 125}{(7x - 5)(x + 4)} $		
    						\item  $ \dfrac{7x - 4y}{8y} $
    						\item  $ \dfrac{x + 2}{(x - 2)^2} $
    						\item  $ \dfrac{6 + 5x}{x^2 + 3x + 2} $
    					\end{multicols}
    	\end{enumerate}}}} 
    \end{center}
    
    \begin{enumerate}[resume]
    	\begin{multicols}{2}
    		\item  $ \dfrac{x - y}{8y} + \dfrac{6x - 3y}{8y} $			
    		\item  $ \dfrac{x - 3y}{6x^3y} - \dfrac{x + 3y}{6x^3y} $			
    		\item  $ \dfrac{5}{x^2 + 3x + 2} + \dfrac{5x + 1}{x^2 + 3x + 2} $			
    		\item  $ \dfrac{x + 2}{2x^2 + 13x + 20} - \dfrac{x + 3}{2x^2 + 13x + 20} $			
    		\item  $ \dfrac{x + 6}{3x - 6} + \dfrac{x + 1}{3x - 6} $			
    		\item $ \dfrac{2x}{x^2 - 4x + 4} - \dfrac{1}{x - 2} $						 	
    		\item $ 6 - \dfrac{x + 5}{(7x - 5)(x + 4)} $				 	
    		\item $ \dfrac{2}{3x^2 + 12x} + \dfrac{8}{2x} $					 	
    		\item $ \dfrac{5x + 5}{5x^2 + 35x - 40} + \dfrac{7x}{3x} $					 	
    		\item $ \dfrac{4}{x + 1} - \dfrac{2}{x + 2} $			
    	\end{multicols}
    \end{enumerate}
    %\vspace*{1.3ex}
    \newpage
    
    \noindent \textbf{C. Solving Problems on Rational Algebraic Expressions} 
    
    Solve each problem completely. Choose the answer from the box. Write the letter only. One point each.
    
    \begin{center} \fbox{\fbox{\parbox{4.5in}{\centering \begin{enumerate}[label=\alph*. ]
    					\begin{multicols}{2}
    						\item $ \dfrac{24}{5} $	%a
    						\item $ 1 $	%b
    						\item $ \dfrac{270}{7} $	%c
    						\item $ 60 $	%d
    						\item $ \dfrac{12}{5} $	%e
    						\item $ 6 $	%f
    						\item $ \dfrac{40}{3} $	%g
    						\item $ 30 $	%h
    						\item $ \dfrac{1}{15} $	%i
    						\item $ 33 $	%j				
    					\end{multicols}
    	\end{enumerate}}}} 
    \end{center}
    
    \begin{enumerate}[resume]
    	%\begin{multicols}{2}
    	\item Mario needs 4 hours to complete a work. His friend Juvan needs 6 hours to complete the same work. How long will it take to complete if they work together?	%1
    	\item The ratio of girls to boys at Maria's school is $ 2:3 $. If there are 22 girls at Maria's school, how many boys are there?	%2
    	\item Suppose one painter can paint the entire house in twelve hours, and the second painter takes eight hours to paint a similarly-sized house. How long would it take the two painters together to paint the house?	%3
    	\item Wilma can mow the lawn in 3 hours. If Kyle helps her with another mower, the lawn can be mowed in 2 hours. How long would it take Kyle if he worked alone? 	%4
    	\item The ratio of an angle to its complement is $ \dfrac{3}{4} $. Find the angle.	%5
    	\item Find a number which when added to both the numerator and denominator of $ \dfrac{2}{5} $ will make the fraction equal to $ \dfrac{1}{2} $.	%6
    	\item When 10 is subtracted from the reciprocal of a number, the result is 5. What is the number?	%7
    	\item Jessica can do her project in 20 minutes and Michelle can do the same work in 40 minutes. How long will it take them to finish the same work if they work together?	%8
    	\item The sum of $ \dfrac{1}{5} $ of a certain number and $ \dfrac{1}{3} $ of the same number is 32. Find the number. %9
    	\item A filler pipe can fill a tank in 10 hours, while an outlet pipe can empty the tank in 15 hours. How long would it take to fill the empty tank with both pipes operating?	%10			
    	%\end{multicols}
    \end{enumerate}
    
\end{document}