\documentclass[14pt]{beamer}
\input{../beamer-preamble-2020}
\usetheme{default}
\usecolortheme{seahorse}


\title[Factoring the Diff. of Squares] {Factoring the Difference of Two Squares}
\author{Jonathan R. Bacolod}
\institute[SHS]{Sauyo High School}
\date{}

\begin{document}
	\frame{\titlepage}
	
	\begin{frame}
		\frametitle{What is a Perfect Square?}
		When a polynomial is multiplied by itself, then it is a perfect square.  
	\end{frame}

    \begin{frame}
    	\frametitle{What is a Difference of Two Squares?}
    	The difference of two squares is a squared polynomial subtracted from another squared polynomial.  
    \end{frame}

    \begin{frame}
    	\frametitle{How to Determine if a Binomial is a Difference of Two Squares?}
    	\begin{enumerate}
    		\item<1-> Factor out the Greatest Common Monomial Factor (GCMF).
    		\item<2-> Is the first term a perfect square?
    		\item<3-> Is the second term a perfect square?
    		\item<4-> Do the terms have subtraction as the operation?
    	\end{enumerate} 
    \end{frame}

    \begin{frame}
    	\frametitle{How to Factor the Difference of Two Squares?}
    	Use the formula:
    	\[ a^2 - b^2 = (a+b)(a-b) \]
    	\begin{center}
    		or 
    	\end{center}
        \[ \text{1st}^2 - \text{2nd}^2 = (\text{1st} + \text{2nd})(\text{1st} - \text{2nd}) \]
    
    \end{frame}

    \begin{frame}
    	\frametitle{How to Factor the Difference of Two Squares?}
    	\begin{enumerate}
    		\item<1-> Factor out the Greatest Common Monomial Factor (GCMF).
    		\item<2-> Write the first term as a perfect square.
    		\item<3-> Write the second term as a perfect square.
    		\item<4-> Factor it out as a product of two binomials with alternating signs in the middle, positive and negative.
    		\item<5-> Factor out any binomial that can still be factored further.
    	\end{enumerate} 
    \end{frame}

    \begin{frame}
    	\begin{center}
    		\textbf{\LARGE Thank you for watching.}
    	\end{center}
    \end{frame}
	
\end{document}