\documentclass[14pt]{beamer}
\input{../../../beamer-preamble-2020}
\usetheme{default}
\usecolortheme{seahorse}


\title[] {Solving Problems Involving Factors of Polynomials}
\author{Jonathan R. Bacolod}
\institute[SHS]{Sauyo High School}
\date{}

\begin{document}
	\frame{\titlepage}
	
	\begin{frame}
		\frametitle{What is the Zero Product Property?}
			If the product of two factors is zero, then one or both factors must be zero.\\
			In symbols, for all real numbers $ a $ and $ b $, if $ ab = 0 $, then $ a = 0 $ or $ b = 0 $ or both $ a $ and $ b = 0 $.
	\end{frame}
	
	\begin{frame}
		\frametitle{How to Solve Word Problems Involving Factors of Polynomials?}
		\begin{enumerate}
			\item<1-> Understand the problem.
			\begin{enumerate}
				\item<1-> Represent the unknown quantities.
			\end{enumerate}
		    \item<2-> Write an equation.
		    \item<3-> Solve the equation.
		    \item<4-> Interpret the results.
		    \begin{enumerate}
		    	\item<4-> Verify if your answer makes sense. 
		    \end{enumerate}
		\end{enumerate}	
	\end{frame}

    \begin{frame}
    	\frametitle{Reminder}
    	A negative number cannot be considered as length, width, or
    	age. So, you need to reject an answer that does not satisfy
    	the conditions stated in each problem.
    \end{frame}

   \begin{frame}
   	\frametitle{Sample Problem 1}
   	The length of a rectangular frame is 4 cm more than the width. If the
   	area of the frame is 60 square cm, how long is the frame?
   \end{frame}

    \begin{frame}
    	\frametitle{Sample Problem 2}
    	The square of a number is 20 more than 8 times the number. Find the
    	number.
    \end{frame}

    \begin{frame}
    	\frametitle{Sample Problem 3}
    	The ages of Rosita and Adelaida are consecutive even integers.
    	Rosita is older than Adelaida. If the sum of the squares of their ages is
    	340, how old is Rosita?
    \end{frame}

    \begin{frame}
    	\begin{center}
    		\textbf{\LARGE Thank you for watching.}
    	\end{center}
    \end{frame}
	
\end{document}