\input{../../worksheets-preamble-2020}

\def \Lesson {Solving Problems Involving Factors of Polynomials}

\begin{document}
	\begin{center}
		\textbf{\large Practice Exercises on \Lesson}
	\end{center}

    \vspace*{2em}

    \noindent \textbf{A. Representing Quantities} \\
    
    Convert each statement into algebraic expressions. One point each.
    
    \begin{enumerate}
    	%\begin{multicols}{2}
    	\item The sum of a positive number and its square is 12.
    	\item The length of a rectangular piece of paper is 8 cm more than its width. 
    	\item The square of a number equals 7 times that number. 
    	\item The ages of two children are consecutive odd integers. 
    	\item The cube of a number equals 11 times that number. 
        %\end{multicols}
    \end{enumerate}

    \vspace*{1.3ex}

    \noindent \textbf{B. Problem Solving} \\
    
    Solve each problem completely. Write the final answers only. One point each.
    
    \begin{enumerate}
    	%\begin{multicols}{2}
    	\item A rectangular lot is 8 meters longer than it is wide. The area of the lot is 65 squares meters. Find the length of the lot.
       	\item The square of a positive number equals 10 times that number. Find the number.
    	\item The ages of two children are consecutive even integers. If the product of their ages is	80, how old is the younger child?
    	\item Find two odd consecutive integers whose product is 143.
    	\item The sum of a positive number and its square is 90. Find the number.
    	\item The length of a rectangular piece of paper is 11 cm more than its width. Its area is 42 square centimeters. How long is the piece of paper?
    	\item A rectangular lot is 4 meters longer than its width. The area of the lot is 77 square meters. Find the length of the lot.
    	\item The square of a positive number equals 5 times that number. Find the number.
    	\item The ages of two children are consecutive even integers. If the product of their ages is	120. How old is the younger child?
    	\item Find two consecutive odd integers whose product is 99.
    	       %\end{multicols}
    \end{enumerate}

    \newpage
    
     \noindent\rotatebox[origin=b]{180}{\noindent\begin{minipage}{\textwidth}
    
    \begin{center}
    	\textbf{\large Answer Key}
    \end{center}
    
    \vspace*{2em}
    
    \noindent \textbf{A. Representing Quantities} \\
    
    \begin{enumerate}
    	%\begin{multicols}{2}
    	\item $ x^2 + x = 12 $
    	\item $ l = w + 8 $
    	\item $ x^2 = 7x $ 
    	\item $ x $ and $ x+2 $ 
    	\item $ x^3 = 11x $
    	%\end{multicols}
    \end{enumerate}
    
    \vspace*{1.3ex}
    
    \noindent \textbf{B. Problem Solving} \\
        
    \begin{enumerate}
    	%\begin{multicols}{2}
    	\item 13 meters
    	\item 10
    	\item 8 years old
    	\item 11 and 13
    	\item 9
    	\item 14 cm
    	\item 11 m
    	\item 5
    	\item 10 years old
    	\item 9 and 11
    	%\end{multicols}
    \end{enumerate}
    \end{minipage}}
\end{document}